Discrete Ordinates

### 2016-11-16 docprep/draft1.tex
Added a whopping 4 words
Added the Plm recurrance equations
Replaced \cdot with x in the double factorial equation because it was hard to see.
Finished the sweep() routine

Given:
\begin{itemize}
\item A list of all energies, $\mathcal{E}$
\item A list of all directions in the quadrature, $Q$
\item A mapping from $r$ to zone number, $\mathcal{Z}(r)$
\item Lists of direction cosines, $\mu$, $\xi$, and $\eta$
\item A map of $r$ to voxel volume, $V(r)$
\item A list of all $x$, $y$, and $z$ voxel centers, $X$, $Y$, and $Z$
\item A list of weights for the quadrature, $\omega$
\item A list of scatter cross sections in zone $\mathcal{Z}(r)$ from energy $E'$ to $E$, $\Sigma_s(\mathcal{Z}(r), E', E)$
\item A list of total cross sections in zone $\mathcal{Z}(r)$ at energy $E$, $\Sigma_T(\mathcal{Z}(r), E)$
\item The surface area of all voxels, $A_{xy}(r)$, $A_{yz}(r)$, $A_{xz}(r)$
\end{itemize}

@@

  (*$\phi(r, E) = \vec{0}$*)    # Scalar flux
  (*$\Psi(r, \Omega, E) = \vec{0}$*)  # Angular flux

  for (*$E \in \mathcal{E}$*) in descending order
    while not converged
      for (*$\Omega \in Q$*) in any order
        if (*$\mu(\Omega) > 0$*) and (*$\xi(\Omega) > 0$*) and (*$\eta(\Omega) > 0$*)
          octant1()
        else if (*$\mu(\Omega) > 0$*) and (*$\xi(\Omega) > 0$*) and (*$\eta(\Omega) < 0$*)
          octant2()
        ...
        else
          octant8()
\end{lstlisting}

@@

@@

>>>>

Given:
\begin{itemize}
\item A list of all energies, $\{E\}$
\item A list of all directions in the quadrature, $\{\Omega\}$
\item A mapping from $r$ to zone number, $\mathcal{Z}(r)$
\item Lists of direction cosines, $\mu(\Omega)$, $\xi(\Omega)$, and $\eta(\Omega)$
\item A map of $r$ to voxel volume, $V(r)$
%\item A list of all $x$, $y$, and $z$ voxel centers, $X$, $Y$, and $Z$
\item A mapping of weights for the quadrature, $\omega(\Omega)$
\item A mapping of scatter cross sections in zone $\mathcal{Z}(r)$ from energy $E'$ to $E$, $\Sigma_s(\mathcal{Z}(r), E' \rightarrow E)$
\item A list of total cross sections in zone $\mathcal{Z}(r)$ at energy $E$, $\Sigma_T(\mathcal{Z}(r), E)$
\item The surface area of all voxels, $A_{xy}(r)$, $A_{yz}(r)$, $A_{xz}(r)$
\end{itemize}

@@

  # Knowns
  (*$V(r)$*)  # [cm^3] volume of cell ijk
  (*$A_{xy}(\Omega,i,j), A_{yz}(\Omega,j,k), A_{xz}(\Omega,i,k)$*)  # [cm^2] Area of each face of cell ijk
  # Unknowns
  (*$\phi(r, E) = \vec{0}$*)    # Scalar flux
  (*$\Psi(r, \Omega, E) = \vec{0}$*)  # Angular flux

  for every (*$E \in \{E\}$*) in descending order
    while not converged
      (*$\phi^{i-1}(r) = \phi^{i+1}(r)$*)
      (*$S(r) = \vec{0}$*)
      for every (*$E' >= E$*)
        for every cell (*$ijk$*)
          (*$S(ijk) = S(ijk) + 1/4\pi \phi(E', ijk)*\Sigma_s(\mathcal{Z}(ijk), E')*V(ijk)$*)
      for every cell (*$ijk$*)
        (*$S(ijk) = S(ijk) + S_{x}(ijk)$*)
      (*$\phi^{i+1} = \vec{0}$*)
      for every (*$\Omega \in Q$*) in any order
        (*$i_0 = f(\mu(\Omega))$*)
        (*$\Delta i = f(\mu(\Omega))$*)
        (*$j_0 = f(\xi(\Omega))$*)
        (*$\Delta j = f(\xi(\Omega))$*)
        (*$k_0 = f(\eta(\Omega))$*)
        (*$\Delta k = f(\eta(\Omega))$*)
        for every cell (*$ijk$*) starting at (*$(i_0, j_0, k_0)$*) in direction (*$<\Delta i, \Delta j, \Delta k>$*)
          if (*$i \in \partial$*)
            (*$\phi_{x+} = 0$*)
          else
            (*$\phi_{x+} = \phi_{x-}(i\pm 1, j, k)$*)    
          if (*$j \in \partial$*)
            (*$\phi_{y+} = 0$*)
          else
            (*$\phi_{y+} = \phi_{y-}(i, j \pm 1, k)$*) 
          if (*$k \in \partial$*)
            (*$\phi_{z+} = 0$*)
          else
            (*$\phi_{z+} = \phi_{z-}(i, j, k \pm 1)$*)

          (*$n = S(ijk) + A_{yz}(\Omega, j,k)\phi_{x+} + A_{xz}(\Omega, i, k) \phi_{y+} + A_{xy}(\Omega, i,j)\phi_{z+}$*)
          (*$d = V(ijk)*\Sigma_t(\mathcal{Z}(ijk), E) + A_{yz}(\Omega, j, k) + A_{xz}(\Omega, i, k) + A_{xy}(\Omega, i, j)$*)
          (*$\Psi_0 = n/d$*)
          (*$\Psi(E, \Omega, ijk) = \Psi_0$*)
          (*$\phi_{x-}(ijk) = 2\Psi_0 - \phi_{x+}$*)
          (*$\phi_{y-}(ijk) = 2\Psi_0 - \phi_{y+}$*)
          (*$\phi_{z-}(ijk) = 2\Psi_0 - \phi_{z+}$*)
          (*$\phi^{i+1}(ijk) = \phi^{i+1} + \omega(\Omega)\Psi(e, \Omega, ijk)$*)
        for every cell (*$ijk$*)
          (*$\phi(E, ijk) = \phi^{i+1}(ijk)$*)
        EMIT (*$\phi(E, ijk)$*)
      (*$\epsilon = max((\phi^{i+1} - phi^{i-1})/\phi^{i+1})$*)

      for every cell (*$ijk$*)
        (*$\phi(E, ijk) = \phi^{i+1}(ijk)$*)
  output time to completion
\end{lstlisting}

@@

The real part of the

@@

Some useful recurrence relations used to calculate the Associated Legendre Polynomials are:

\begin{equation}
P_l^l(x) = (-1)^l(2l-1)!!(1-x^2)^(l/2)
\end{equation}

\begin{equation}
P_{l+1}^l(x) = x(2l+1)P_l^l(x)
\end{equation}

\begin{equation}
P_l^l(x) = (-1)^l(2l-1)!!(1-x^2)^(l/2)
\end{equation}

where $x!!$ is the double factorial function defined by:

\begin{equation}
x!! = \prod_{k=0}^{\lceil x/2 \rceil - 1} x-2k
\end{equation}

For example, $5!! = 5 \times 3 \times 1 = 15$.
